Simulations

### 2020-12-08 Simulations.Rmd

# Simulating a season
```{r}
simulateSeason <- function() {
  # Start all teams at 
  teamPoints <- rep(0, 30)
  for (game in 1:dim(data[1])) {
    homeTeam <- getHomeTeam(game)
    awayTeam <- getAwayTeam(game)
    # Extract game performance values
    homePerformance <- rnorm(teamQuality[homeTeam], tao)
    awayPerformance <- rnorm(teamQuality[awayTeam], tao)

    # Check if there is a tie
    tie <- abs(homePerformance - awayPerformance)

    # If the game did not go into overtime award points
    if (tie >= alpha) {
      if (homePerformance > awayPerformance) {
        teamPoints[homeTeam] = teamPoints[homeTeam] + 2
      }
      else {
        teamPoints[awayTeam] = teamPoints[awayTeam] + 2
      }
    }
    # If the game did go into overtime simulate outcome of overtime
    else {

    }

  }
}
```

# Helper function
```{r}
getHomeTeam <- function(index) {
  return (data$home_team_id[index])
}

getAwayTeam <- function(index) {
  return (data$away_team_id[index])
}
```

>>>>

# Simulating a season
```{r}
simulateSeason <- function() {
  # Create overall games matrix with format:
  # GAME | TEAM 1 | TEAM 2 | GAMMA 1 | GAMMA 2 | GAMMA 1 - GAMMA 2 | OUTCOME 1 | OUTCOME 2
  # Where 'outcome' is the number of points awarded to their respective teams
  games <- list(seq(1, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]), rep(0, dim(data[1])[1]))

  # Go through the games
  for (game in 1:length(games[[1]])) {

    # Get the teams for each game and put them in the games matrix
    homeTeam <- getHomeTeam(game)
    awayTeam <- getAwayTeam(game)

    games[[2]][game] <- homeTeam
    games[[3]][game] <- awayTeam

    # Extract game performance values -- insert into games matrix
    homePerformance <- rnorm(n = 1, teamQuality[homeTeam], tao)
    awayPerformance <- rnorm(n = 1, teamQuality[awayTeam], tao)

    games[[4]][game] <- homePerformance
    games[[5]][game] <- awayPerformance

    # Check if there is a tie -- store difference for later
    games[[6]][game] <- homePerformance - awayPerformance
  }
  a <- mean(games[[6]])
  b <- max(games[[6]])

  # Go through and calculate outcomes
  for (game in 1:length(games[[1]])) {
    # If there is a tie award 2 points to the 'winner'
    if (abs(games[[6]][game]) >= alpha) {
      if (games[[6]][game] >= 0) {
        games[[7]][game] <- 2
      }
      else {
        games[[8]][game] <- 2
      }
    }
    # Else rescale performances and simulate a winner, giving two points to the winner and one to the loser
    else {
      zeta <- (games[[6]][game] - a) / b
      if (rbernoulli(1, p = zeta)) {
        games[[7]][game] <- 2
        games[[8]][game] <- 1
      }
      else {
        games[[7]][game] <- 1
        games[[8]][game] <- 2
      }
    }
  }

}
```

# Helper functions
```{r}
getHomeTeam <- function(index) {
  return (data$home_team_id[index])
}

getAwayTeam <- function(index) {
  return (data$away_team_id[index])
}

overtime <- function() {

}
```
